Ornaments as indicators of social changes resulting from indirect effects of colonialism in northeastern Taiwan

### 2020-09-22 analysis/paper/paper.Rmd
replace figure 3 to avoid text overlapping with curve

                               # Use Bchron to calibrate
library(Bchron)

@@

ggsave(plot = kwl_ages_curve,
       here("analysis", "figures",
       "plot-c14-ages-distribution.jpg"),
       width = 120, 
       dpi = 300,
       height = 62,
       units = "mm")

>>>>

# Use Bchron to calibrate
# need github version to get intcal20
# if(!require(remotes)) install.packages('remotes')
# remotes::install_github('andrewcparnell/Bchron')
library(Bchron)

@@

ggsave(plot = kwl_ages_curve,
       here("analysis", "figures",
       "plot-c14-ages-distribution.jpg"),
       width = 120, 
       dpi = 300,
       height = 100,
       units = "mm")
